\documentclass[a4paper]{article}
\usepackage[utf8x]{inputenc}
\usepackage{amsmath}
\usepackage[english]{babel}
\usepackage[a4paper, top=3cm, bottom=2cm, left=3cm, right=3cm, marginparwidth=1.75cm]{geometry}

% Title Page
\title{Group 24 Project Approval}
\date{2017/09/20}

\begin{document}
\maketitle

% Turns off numbering for sections
\setcounter{secnumdepth}{0}

\newpage

% Information regarding team
\section{Team Info}
Team Name: Reminders \\%TODO
Members: \\
Bishoy Sefin - sefinb \\
Michael Panunto - panuntom \\
Michael Jenkins - jenkinma \\

% Information regarding original project, and scope of the software
\section{Original Project}
Original Project Name: Remember Me\\
https://github.com/blairkutz/rememberme
~\\~\\
\noindent This software is designed to act as a reminder system for users. After setting up the application it will e-mail you at a specified time to remind you about upcoming/recurring events. Users can reply to the email system to have the response saved for future reference. The email is sent from your account, to your account.

% How we plan to change the project
\section{Redevelopment of the Project}

The original project was designed as a google application (web based), however we plan to redevelop it for android while implementing additional features including automated email messages depending on the event given. Since we are developing for android, an android device would be the only hardware requirements, emulators are available for computers if necessary.
~\\~\\
There are no software licenses required.  
~\\~\\
The original application was developed using HTML and Google App Scripts, all three members of the group are familiar with HTML, while Google App Scripts is new to us, although it is similar to javascript. However, since we are developing this as an android application we only need to know Google App Script to understand the code and it is well documented; Other than that we all know XML and Java which are the required languages for Java. 
~\\~\\
Yes, the domain knowledge for the project is understandable within the term. The project is not very complex which means that with some work and effort the team should be able to complete the project. 
~\\~\\
The are 8 different source code files totalling to 1094 Lines of code. 
~\\~\\
Apache Licence \\
Version 2.0, January 2004\\
http://apache.org/licences/\\
https://github.com/blairkutz/rememberme/blob/master/LICENSE
~\\~\\
Yes the licence does allow public redevelopment
~\\~\\
The source code can be run at https://github.com/blairkutz/rememberme\#setting-up
~\\~\\
Testing: Test cases would involve invalid time entries, and the use of an invalid email address as well as using special characters within the input fields.

\end{document}